Distributed multi-objective evolutionary optimization using island-based selective operator application

### 2019-05-07 hpmoon-asoco.tex
Added blue to @JJ 's changes, after removing all the previous blue

Usually an EA starts by generating a \emph{population}, that is, a set of random solutions, following a user-defined description. Then, it
evaluates each candidate solution, called \emph{individual}, assigning
it a \emph{fitness} value that describes how good the individual is
solving the target problem. New solutions are then generated by
the application of \emph{operators} that either mutate a single
solution or recombine different existing solutions. After each
iteration, called \emph{generation}, the least fit individuals are
removed, and the process continues until a user-defined stop condition
is met.

EAs were extended to multi-objective optimization through quite a number of Multi-Objective Evolutionary Algorithms (MOEAs) \cite{TalbiUnified2018}.
One of the best known and referenced MOEAs
\citep{Dorronsoro13superlinear} is the {\em 
  Non-dominated Sorting Genetic Algorithm} (NSGA-II)
\citep{Deb00NSGAII}. Classical genetic operators are applied to all
the individuals, which are divided into different ranks, based on 
dominance, to be selected for the next generations.

@@

In our previous work \citep{Garcia16hpmoon} we used this method in a
preliminary experimental setup, although it is worth mentioning we are
establishing its name and acronym in this paper for the first time.
We show
that applying the variation operators only over specific sections of the whole chromosome improves the quality of the solutions in the same computing time for a multi-objective island-based algorithm.
Moreover, instead of making every island focus on a disjoint subset of the
chromosome, the usage of overlapped (shared) sections of the
chromosome 
can improve the quality of the solutions 
when the number of islands is increased. In that paper, we showed that the most
adequate overlapping size may vary depending on a relation between the
number of islands and the individual size. However, it was a proof-of-concept, and the experiments
were conducted in a limited experimental system: mono-processor and
synchronous island model. 
This
motivates us to continue this research line using a more complete environment: a real cluster with up to 128 nodes, and a more extensive parameter evaluation. Besides comparing previous methods in this new experimental setup, in this paper we propose
a new method that automatically sets the size of the overlapped
sections depending on the number of available islands, comparing it with previous versions.

>>>>

Usually an EA starts by generating \textcolor{blue}{a \emph{population}, that is, a set of random solutions}, following a user-defined description. Then, it
evaluates each candidate solution, called \emph{individual}, assigning
it a \emph{fitness} value that describes how good the individual is
\textcolor{blue}{solving} the target problem. New solutions are then generated by
the application of \emph{operators} that either mutate a single
solution or recombine different existing solutions. After each
iteration, called \emph{generation}, the least fit individuals are
removed, and the process continues until a user-defined stop condition
is met.

EAs \textcolor{blue}{were} extended to multi-objective optimization through quite a number of Multi-Objective Evolutionary Algorithms (MOEAs) \cite{TalbiUnified2018}.
One of the best known and referenced MOEAs
\citep{Dorronsoro13superlinear} is the {\em 
  Non-dominated Sorting Genetic Algorithm} (NSGA-II)
\citep{Deb00NSGAII}. Classical genetic operators are applied to all
the individuals, which are divided into different ranks, based on 
dominance, to be selected for the next generations.

@@

In our previous work \citep{Garcia16hpmoon} we used this method in a
preliminary experimental setup, although it is worth mentioning we are
establishing its name and acronym in this paper for the first time.
We show
that applying the variation operators only over specific sections of the whole chromosome improves the quality of the solutions in the same computing time for a multi-objective island-based algorithm.
Moreover, instead of making every island focus on a disjoint subset of the
chromosome, the usage of overlapped (shared) sections of the
chromosome 
can improve the quality of the solutions 
when the number of islands is increased. In that paper, we showed that the most
adequate overlapping size may vary depending on a relation between the
number of islands and the individual size. However, it was a proof-of-concept, and the experiments
were conducted in a limited experimental system: mono-processor and
synchronous island model. 
This
motivates us to continue this research line using a more complete environment: a real cluster with up to 128 nodes, and a more \textcolor{blue}{extensive parameter evaluation}. Besides comparing previous methods in this new experimental setup, in this paper we propose
a new method that automatically sets the size of the overlapped
sections depending on the number of available islands, comparing it with previous versions.
